\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-24 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

For completeness, the proximal algorithm for updating $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}\mapsto\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ is outlined in Algorithm \ref{algo:KineticProx}. Its convergence guarantees can be found in \cite[Sec. III.C]{caluya2019TAC}.

@@

\begin{IEEEbiography}[{\includegraphics[height=1.25in]{Abhishek-Halder.jpg}}]{Abhishek
Halder}
(S'10-M'14) is an Assistant Professor in the Department of Applied Mathematics,
and is an affiliated faculty in the Department of Electrical and Computer Engineering at
University of California, Santa Cruz. Before that he held postdoctoral
positions in the Department of Mechanical and Aerospace Engineering at
University of California, Irvine, and in the Department of Electrical
and Computer Engineering at Texas A\&M University. He obtained his
Bachelors and Masters from Indian Institute of Technology Kharagpur in
2008, and Ph.D. from Texas A\&M University in 2014, all in Aerospace
Engineering. His research interests are in stochastic systems, control
and optimization with application focus on large scale cyber-physical
systems.
\end{IEEEbiography}

>>>>

For completeness, the proximal algorithm for updating $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}\mapsto\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ is outlined in Algorithm \ref{algo:KineticProx}. As shown in Fig. \ref{fig:BlockDiagm}, this algorithm takes the pre and post update state samples 
\[\{\tilde{\bm{x}}_{k-1}^{i}\}_{i=1}^{N}\equiv\{\left(\bm{\xi}_{k-1}^{i},\bm{\eta}_{k-1}^{i}\right)\}_{i=1}^{N}, \; \{\tilde{\bm{x}}_{k}^{i}\}_{i=1}^{N}\equiv\{\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)\}_{i=1}^{N},\]
and $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}$ as inputs. The Algorithm \ref{algo:KineticProx} has additional

Its convergence guarantees can be found in \cite[Sec. III.C]{caluya2019TAC}.

@@

\begin{IEEEbiography}[{\includegraphics[height=1.25in]{Abhishek-Halder.jpg}}]{Abhishek
Halder}
(S'10-M'14) is an Assistant Professor in the Department of Applied Mathematics,
and is an affiliated faculty in the Department of Electrical and Computer Engineering at
University of California, Santa Cruz. Before that he held postdoctoral
positions in the Department of Mechanical and Aerospace Engineering at
University of California, Irvine, and in the Department of Electrical
and Computer Engineering at Texas A\&M University. He obtained his
Bachelors and Masters from Indian Institute of Technology Kharagpur in
2008, and Ph.D. from Texas A\&M University in 2014, all in Aerospace
Engineering. His research interests are in stochastic systems, control, learning and optimization with application focus on large scale cyber-physical
systems.
\end{IEEEbiography}
